Choosing TTC Subway Service Provides the Most Time Stability during Weekday Rush-Hours

### 2024-09-26 outputs/paper/paper.qmd
updated wording of abstract and intro

---
title: "Choosing TTC Subway Service Provides the Most Time Stability during Weekday Rush-Hours"
subtitle: "Analysis on the Delay Magnitude of different TTC Services"
author: 
  - Sandy Yu
thanks: "Code and data are available at: https://github.com/Jingying-yu/ttc_delay.git"
date: today
date-format: long
abstract: "This paper analyzes the magnitude of TTC delays in 2023 based on service types. TTC delay data for buses, streetcars, and subways are obtained through Open Data Toronto data portal and data is used to visualize delay magnitude during different days and hours throughout the year. We find that, although TTC streetcars offered the least number of delays in 2023, riding on TTC subways provides the least average time of delay during weekday rush-hour traffic. Our results suggest that, if the time required to arrive at one's office is the same for all TTC service options, choosing subway over other services could provide the most time stability."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

@@

Public transportation serves as the transportation backbone for city  residents, facilitating the daily commute of millions of people. For office workers, students, and the elderly, selecting the appropriate TTC service is crucial in maintaining a reliable and efficient schedule. Despite the importance of this choice, there has been limited effort to evaluate the reliability of different TTC services to guide commuters’choices.

>>>>

---
title: "Choosing TTC Subway Service Provides the Most Time Stability during Weekday Rush-Hours"
subtitle: "Analysis on the Delay Magnitude of different TTC Services"
author: 
  - Sandy Yu
thanks: "Code and data are available at: https://github.com/Jingying-yu/ttc_delay.git"
date: today
date-format: long
abstract: "This paper analyzes the magnitude of TTC delays in 2023 based on service types. Delay data for buses, streetcars, and subways are obtained through Open Data Toronto and the data collected are used to visualize delay magnitude during different days and hours throughout the year. We find that, although TTC streetcars offered the least number of delays in 2023, riding on TTC subways provides the least average time of delay during weekday rush-hour traffic. Our results suggest that, if the time required to arrive at one's office is the same for all TTC service options, choosing subway over other services could provide the most time stability."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

@@

Public transits serves as the transportation backbone for city  residents, facilitating the daily commute of millions of people. For office workers, students, and the elderly, selecting the appropriate TTC service is crucial in maintaining a reliable and efficient schedule. Despite the importance of this choice, there has been limited effort to evaluate the reliability of different TTC services to guide commuters’choices.
